\proglang{EpiCompare}: Working title

### 2020-05-14 jss/jss-article-rnw/chapters/ch1-intro-v2.Rnw
similar change to Rnw

The goal of \pkg{EpiCompare} is not to supplant existing infectious disease modeling tools and software but, rather, is a concerted effort to create standard and fair comparisons among models developed for disease outbreaks and outbreak data. \ben\{pkg{EpiCompare}'s major unique contribution to the existing approaches is a set of time-free tools (motivated in more detail in Section \ref{sec:time-free}).} \ben{More broadly,\sout{To this end,}} \pkg{EpiCompare} \ben{aids the data analysis pipeline for infecetious diseases by}
\begin{enumerate}
  \item Standardiz\ben{\sout{es}ing} outputs from common \ben{\proglang{R}-based} infectious disease model software \ben{\sout{as a form of data pre-processing} and common data storage types}
  \item \ben{\sout{Complements existing software for data visualization and EDA} Expanding upon existing data visualization and EDA tools}
  \item Provides support for modeling and simulation\ben{\footnote{\ben{What are you trying to say here?}}}
  \item \ben{\sout{Harmonizes data and model formats to be used in conjunction with one another}\footnote{\ben{I think this is the same as the first bullet?}}}
  \item \ben{Aiding in comparison and assessment of \sout{Assesses}} models through time free analysis and conformal prediction bands and comparisons.
\end{enumerate}
Although \pkg{EpiCompare} aids in every part of the pipeline, our tools especially emphasize improvements for pipeline parts (1), (4), and (5) which can be summarized as data input and output harmonization and contributions to fairly comparing models and data to one another.

>>>>

The goal of \pkg{EpiCompare} is not to supplant existing infectious disease modeling tools and software but, rather, is a concerted effort to create standard and fair comparisons among models developed for disease outbreaks and outbreak data. \ben
{\pkg{EpiCompare}'s major unique contribution to the existing approaches is a set of time-free tools (motivated in more detail in Section \ref{sec:time-free}).} \ben{More broadly,\sout{To this end,}} \pkg{EpiCompare} \ben{aids the data analysis pipeline for infecetious diseases by}
\begin{enumerate}
  \item Standardiz\ben{\sout{es}ing} outputs from common \ben{\proglang{R}-based} infectious disease model software \ben{\sout{as a form of data pre-processing} and common data storage types}
  \item \ben{\sout{Complements existing software for data visualization and EDA} Expanding upon existing data visualization and EDA tools}
  \item Provides support for modeling and simulation\ben{\footnote{\ben{What are you trying to say here?}}}
  \item \ben{\sout{Harmonizes data and model formats to be used in conjunction with one another}\footnote{\ben{I think this is the same as the first bullet?}}}
  \item \ben{Aiding in comparison and assessment of \sout{Assesses}} models through time free analysis and conformal prediction bands and comparisons.
\end{enumerate}
Although \pkg{EpiCompare} aids in every part of the pipeline, our tools especially emphasize improvements for pipeline parts (1), (4), and (5) which can be summarized as data input and output harmonization and contributions to fairly comparing models and data to one another.
